Manuscript draft

### 2019-09-09 manuscript/manuscript draft.Rmd
updated manuscript draft

Analyses were conducted on data contained in the open-access ForC database [@anderson-teixeira_carbon_2016; @anderson-teixeira_forc:_2018]. This database contains records of field-based measurements of forest carbon stocks and annual fluxes, compiled from original publications and existing data compilations and databases. Associated data, such as stand age, measurement methodologies, and disturbance history, are also included. The database was significantly expanded since the publication of [@anderson-teixeira_forc:_2018] through integration with the Global Database of Soil Respiration (SRDB; **Bond-Lamberty, DOI: 10.5194/bg-7-1915-2010**). Additional targeted literature searches were conducted to identify any further available data on primary productivity, with particular focus on mature forests in temperate and boreal regions. ForC currently contains **UPDATE STATS** 29768 records from 5227 plots, representing 20 distinct ecozones across all forested biogeographic and climate zones. We used ForC v.XX, archived on Zenodo with DOI XXX.

>>>>

Analyses were conducted on data contained in the open-access ForC database [@anderson-teixeira_carbon_2016; @anderson-teixeira_forc:_2018]. This database contains records of field-based measurements of forest carbon stocks and annual fluxes, compiled from original publications and existing data compilations and databases. Associated data, such as stand age, measurement methodologies, and disturbance history, are also included. The database was significantly expanded since the publication of [@anderson-teixeira_forc:_2018] through integration with the Global Database of Soil Respiration [@bond-lamberty_global_2010]. Additional targeted literature searches were conducted to identify any further available data on primary productivity, with particular focus on mature forests in temperate and boreal regions. ForC currently contains **UPDATE STATS** 29768 records from 5227 plots, representing 20 distinct ecozones across all forested biogeographic and climate zones. We used ForC v.XX, archived on Zenodo with DOI XXX.
